\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.8cm]{geometry}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

\setmainfont{Times New Roman}
\definecolor{heading}{HTML}{003366}
\definecolor{subtle}{HTML}{555555}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\sloppy
\setlist[itemize]{leftmargin=1.3em, topsep=2pt, itemsep=1pt}

\titleformat{\section}{\large\bfseries\color{heading}}{}{0pt}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{heading}}{}{0pt}{}

\newcommand{\cvitem}[2]{\textbf{#1:} #2\par}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{\nolinkurl{#1}}}
\newcommand{\pub}[6]{%
  \item #1 (#2). #3. \textit{#4}. DOI: \doi{#5}. #6%
}
\newcommand{\project}[4]{%
  \item \textbf{#1} (#2). #3. #4%
}

\begin{document}

{\LARGE \textbf{Wen Quan}}\\[-1pt]
\textcolor{subtle}{Academic CV for Lecturer Positions in Malaysia}\\[3pt]
\href{mailto:wenquan@hngm.edu.cn}{wenquan@hngm.edu.cn} \,|\, 
\href{mailto:wenquan@student.usm.my}{wenquan@student.usm.my} \,|\, 
+86 156-4900-6328 \,|\, +60 12-938-6817\\
Zhengzhou, Henan, China \,|\, ORCID: \href{https://orcid.org/0009-0005-3975-8104}{0009-0005-3975-8104}\\
Academic homepage: \href{https://wenquan0816.github.io/schoolar-site/}{\nolinkurl{wenquan0816.github.io/schoolar-site}}

\section*{Profile}
Current Ph.D. student in Interior Design at the School of Housing, Building and Planning, Universiti Sains Malaysia, with university teaching experience in architectural design, interior design, decorative materials, CAD/BIM, design software, and age-friendly built environment studies. Research focuses on AI-assisted assessment, evidence-based design, age-friendly residential/community/care environments, and design optimization. Publication record includes 6 WoS SCIE/SSCI papers, 3 WoS ESCI papers, and 5 Scopus-indexed papers, with 7 first-author publications and 5 PI-led research projects.

\textbf{Application fit:} Lecturer / Senior Lecturer-track roles in Interior Design, Architecture, Built Environment, Design Technology, Environmental Design, and Age-Friendly Design.

\section*{Key Academic Metrics}
\begin{tabularx}{\textwidth}{>{\bfseries}p{0.36\textwidth}X}
Publications & 14 published journal articles \\
WoS SCIE/SSCI & 6 articles \\
WoS ESCI & 3 articles \\
Scopus-indexed & 5 articles \\
Authorship & 7 first-author articles; 1 second-author corresponding-author article; 6 co-authored articles \\
PI-led projects & 5 research projects \\
Teaching areas & Interior design, decorative materials, architectural design, CAD/BIM, design software, building structures, renovation design \\
\end{tabularx}

\section*{Education}
\begin{itemize}
  \item \textbf{Ph.D. in Interior Design}, School of Housing, Building and Planning, Universiti Sains Malaysia, Malaysia, 2021--Present.
  \item \textbf{Master of Engineering in Architecture}, Henan University of Technology, China, 2014--2017. Specialization: Architectural Design and Theory.
  \item \textbf{Bachelor of Engineering in Architecture}, Anyang Normal University, China, 2009--2014. Dual Degree Program: Bachelor of Education.
\end{itemize}

\section*{Academic Status and Professional Appointments}
\begin{itemize}
  \item \textbf{Current Ph.D. Student}, School of Housing, Building and Planning, Universiti Sains Malaysia, Malaysia, 2021--Present.
  \item \textbf{Secretary}, HBP Postgraduate Student Association, School of Housing, Building and Planning, Universiti Sains Malaysia, 2025--Present.
  \item \textbf{Academic Committee Member and Senior Project Review Expert}, Zhongren Art Museum, Sichuan Province, China, 2020--Present.
  \item \textbf{Lecturer}, Henan Industry and Trade Vocational College, China, 2021--2023.
  \item \textbf{Part-time Lecturer}, Henan University of Animal Husbandry and Economy, China, 2019--2021.
  \item \textbf{Lecturer}, Easton International Art College, Zhengzhou University of Light Industry, China, 2017--2021.
  \item \textbf{Research Associate}, Green Building Research Institute, Henan Academy of Building Research, China, 2017.
\end{itemize}

\section*{Teaching Portfolio}
\textbf{Teaching fields suitable for Malaysian university lecturer applications}
\begin{itemize}
  \item Interior Design; Decorative Materials; Architectural Design.
  \item Engineering Drawing Fundamentals; Architectural Surveying I \& II; Building Structures.
  \item Design Software (Photoshop, Illustrator); Computer-Aided Design (CAD); BIM Software Introduction.
  \item Existing Building Renovation Design; Software Rendering Design; Architectural Space Design.
  \item Architectural Sketching; Architectural Investigation; History of Chinese and Foreign Architecture.
\end{itemize}

\textbf{Teaching context:} undergraduate courses; typical class size approximately 40 students.

\textbf{Information to add before application:} studio/project supervision, assessment responsibilities, and student mentoring outcomes.

\section*{Research Grants and Projects}
\subsection*{PI-Led Research Projects}
\begin{itemize}
  \project{Comprehensive Aging-in-Place Renovation Framework for Legacy Residential Communities in Henan Province}{2022}{Henan Provincial Federation of Social Sciences / Henan Provincial Social Science Research Fund, Project No. SKL-2022-608}{Role: Principal Investigator.}
  \project{Innovative Universal Design Strategies for New Community Development in Henan Province}{2018}{Henan Provincial Federation of Social Sciences / Henan Provincial Social Science Research Fund, Project No. SKL-2018-490, First Prize}{Role: Principal Investigator.}
  \project{Interior Environment Design Strategies for Hospital Outpatient Departments in the Era of Telemedicine}{2020}{Henan Provincial Federation of Social Sciences / Henan Provincial Social Science Research Fund, Project No. SKL-2020-1566}{Role: Principal Investigator.}
  \project{Integrated Healthcare-Housing Model for Community-Based Senior Living Facilities in Zhengzhou}{2018}{Zhengzhou Federation of Social Sciences Research Project, Project No. JX20190146}{Role: Principal Investigator.}
  \project{Adaptive Renovation Strategies for Existing Long-term Care Facilities under COVID-19 Safety Protocols}{2021}{Henan Provincial Department of Education Research Fund, Project No. 2021-ZDJH-433}{Role: Principal Investigator.}
\end{itemize}

\subsection*{Additional Research Projects}
\begin{itemize}
  \project{Sustainable Construction Waste Management and Resource Recovery Research}{2020}{Henan Provincial Department of Education Research Fund, Project No. 2020-ZDJH-477}{Role to confirm.}
  \project{Spatial Planning and Design Framework for Community Early Childhood Centers in Zhengzhou}{2021}{Henan Provincial Department of Education Research Fund, Project No. 2021-ZDJH-429}{Role to confirm.}
\end{itemize}

\section*{Publications}
\subsection*{WoS SCIE/SSCI Publications}
\begin{enumerate}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir}{2026}{A LSTM-based model predictive control method for unlocking the potential of building energy flexibility in Malaysian commercial buildings}{Scientific Reports}{10.1038/s41598-026-53501-8}{WoS SCIE, Q1; first author.}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir; Yanting Wu; Chaojiang Hu}{2026}{AFLE-HIV: developing an age-friendly living environment assessment framework for elderly HIV-infected individuals in China}{BMC Public Health}{10.1186/s12889-026-27748-9}{WoS SCIE, Q1; first author.}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir}{2026}{Transforming vacant rural school buildings into age-friendly facilities under China's aging and low-fertility context: A natural language processing-based evaluation framework}{BMC Geriatrics}{10.1186/s12877-025-06772-1}{WoS SCIE, Q1; first author.}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir}{2025}{A community public health emergency resilience assessment framework based on contrastive learning and hyperbolic embedding}{Frontiers in Public Health}{10.3389/fpubh.2025.1651331}{WoS SSCI, Q1; first author.}
  \pub{Yanli Han; Quan Wen}{2026}{Emotion Recognition in Literary Texts via an Attention-Guided Dual-Stream Gated Fusion Network}{IEEE Access}{10.1109/ACCESS.2026.3686065}{WoS SCIE; second author; corresponding author.}
  \pub{Wenjing Xu; Mazran Ismail; Syafizal Shahruddin; Wen Quan; Yingrui Li}{2025}{Exploring tourists' intentions to adopt augmented reality in cultural heritage museums: Insights from a modified technology acceptance model}{SAGE Open}{10.1177/21582440251339936}{WoS SSCI, Q1; co-author.}
\end{enumerate}

\subsection*{WoS ESCI Publications}
\begin{enumerate}
  \pub{Jia Sheng Zhou; Mohd Jaki Bin Mamat; Quan Wen}{2025}{Analyzing the traditional rural cultural heritage of Lingnan region in China as the foundation for protection and development}{International Journal of Conservation Science}{10.36868/ijcs.2025.01.06}{WoS ESCI, Q1; co-author.}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir}{2024}{Evaluating the residential environment of traditional settlements in northern Jiangxi, China: A multi-dimensional framework}{Journal of Construction in Developing Countries}{10.21315/jcdc.2024.29.s1.11}{WoS ESCI, Q4; first author.}
  \pub{Zhang Jing; Hasnanywati Hassan; Zalena Abdul Aziz; Khoo Terh Jing; Wen Quan}{2025}{Exploring the factors for the use of building information modelling (BIM) in historic buildings}{Journal of Construction in Developing Countries}{10.21315/jcdc.2025.30.s2.14}{WoS ESCI; co-author.}
\end{enumerate}

\subsection*{Scopus-Indexed Publications}
\begin{enumerate}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir; Jing Zhao; Zhang Jing}{2025}{Assessment and prediction model for community resilience in China based on GANs and random forest regression}{Planning Malaysia}{10.21837/pm.v23i38.1823}{Scopus-indexed; first author.}
  \pub{Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir; Jing Zhao; Zhang Jing}{2025}{Developing a comprehensive framework for assessing community resilience to public health emergencies in Henan Province: Insights from SciBERT analysis}{Planning Malaysia}{10.21837/pm.v23i38.1822}{Scopus-indexed; first author.}
  \pub{Yana Zhang; Azizan Marzuki; Bingliang Song; Feifei Zhang; Jiasheng Zhou; Quan Wen; Dahuai Zhao; Qingxin Zhang; Haixin Liu}{2025}{Influencing factors of residents' subjective well-being in rural tourism destinations: A case study of Licha village in Guangdong, China}{Journal of Chinese Architecture and Urbanism}{10.36922/jcau025340068}{Scopus-indexed; co-author.}
  \pub{Jing Zhao; Shida Irwana Omar; Hui Liu; Quan Wen}{2025}{Examining the effects of perceived value on behavioral intention of green tourists in Hulunbuir grassland, China}{Planning Malaysia}{10.21837/pm.v23i36.1752}{Scopus-indexed; co-author.}
  \pub{Jing Zhao; Shida Irwana Omar; Hui Liu; Quan Wen}{2025}{Study on the coupled and coordinated development of tourism economy and ecological environment in Chengdu city, China}{Planning Malaysia}{10.21837/pm.v23i36.1757}{Scopus-indexed; co-author.}
\end{enumerate}

\section*{Professional Service}
\begin{itemize}
  \item Journal Reviewer, \textit{SAGE Open}.
  \item Academic Committee Member and Senior Project Review Expert, Zhongren Art Museum.
\end{itemize}

\section*{Professional Certifications}
\begin{itemize}
  \item Higher Education Teaching Qualification Certificate.
  \item Lecturer Certificate, Zhengzhou University of Light Industry.
  \item National Computer Proficiency Examination Certification.
  \item Network Engineering Professional Certification.
\end{itemize}

\section*{Design Practice}
\begin{itemize}
  \item Principal Design Architect, Comprehensive Library Interior Design Project, Easton Academy of Fine Arts, Zhengzhou University of Light Industry, China, 2020.
  \item Design Architect, Large-scale Agricultural Facility Complex, China Grain Corporation, Yongcheng, Henan, China, 2016.
  \item Design Architect, Sustainable Student Housing Complex, Henan University of Technology, China, 2015.
  \item Design Architect, Integrated Agricultural Development Center, China Grain Corporation, Zhangbei, Hebei, China, 2014.
\end{itemize}

\section*{Honours and Awards}
\begin{itemize}
  \item First Prize Award, Henan Provincial Social Science Federation Research Project Excellence, 2018.
  \item Silver Medal, Henan Provincial Challenge Cup Competition for University Students, 2022.
  \item Silver Medal, 4th International Environmental Sustainability Design Competition, 2020.
  \item Bronze Medals for two student teams, International Environmental Design Competition, 2020.
  \item Bronze Award for Excellence in Mentoring, CADA International Conceptual Design Awards, 2020.
  \item Outstanding Supervision Recognition, ITCD International Design Innovation Competition, 2020.
\end{itemize}

\section*{Languages}
\begin{itemize}
  \item Chinese (Mandarin): Native.
  \item English: Advanced academic and professional proficiency; TOEFL 86/120.
  \item Malay: Conversational proficiency.
\end{itemize}

\section*{Academic Referee}
\begin{itemize}
  \item \textbf{Dr. Mazran bin Ismail}, Senior Lecturer, Architecture, School of Housing, Building and Planning, Universiti Sains Malaysia. Email: \href{mailto:mazran@usm.my}{mazran@usm.my}. Relationship: Ph.D. supervisor.
\end{itemize}

\section*{Information to Confirm Before Submission}
\begin{itemize}
  \item Expected PhD completion date, if required by the application system.
  \item Google Scholar, Scopus Author ID, and Web of Science ResearcherID.
  \item Available start date.
  \item Studio/project supervision, assessment responsibilities, and student mentoring outcomes.
\end{itemize}

\end{document}
