\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.8cm]{geometry}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

\setmainfont{Times New Roman}
\definecolor{heading}{HTML}{003366}
\definecolor{subtle}{HTML}{555555}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\sloppy
\setlist[enumerate]{leftmargin=1.4em, topsep=2pt, itemsep=5pt}

\titleformat{\section}{\large\bfseries\color{heading}}{}{0pt}{}[\titlerule]
\newcommand{\doi}[1]{\href{https://doi.org/#1}{\nolinkurl{#1}}}

\begin{document}

{\LARGE \textbf{Five Representative Publications}}\\[-1pt]
\textbf{Wen Quan}\\
\textcolor{subtle}{Selected for Malaysian University Lecturer Applications}\\
\href{mailto:wenquan@student.usm.my}{wenquan@student.usm.my} \,|\, 
\href{https://wenquan0816.github.io/schoolar-site/}{\nolinkurl{wenquan0816.github.io/schoolar-site}}

\section*{Selection Rationale}
These five publications were selected because they best demonstrate my fit for lecturer roles in Interior Design, Architecture, Built Environment, Design Technology, and Age-Friendly Design. They show a coherent research profile in AI-assisted assessment, age-friendly built environments, public health resilience, computational design methods, and interdisciplinary collaboration. Publication notes do not include impact factors; indexing and authorship roles are provided instead.

\section*{Representative Publications}
\begin{enumerate}
  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2026). \textbf{A LSTM-based model predictive control method for unlocking the potential of building energy flexibility in Malaysian commercial buildings}. \textit{Scientific Reports}. DOI: \doi{10.1038/s41598-026-53501-8}. \textit{WoS SCIE, Q1; first author.}

  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir; Yanting Wu; Chaojiang Hu (2026). \textbf{AFLE-HIV: developing an age-friendly living environment assessment framework for elderly HIV-infected individuals in China}. \textit{BMC Public Health}. DOI: \doi{10.1186/s12889-026-27748-9}. \textit{WoS SCIE, Q1; first author.}

  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2026). \textbf{Transforming vacant rural school buildings into age-friendly facilities under China's aging and low-fertility context: A natural language processing-based evaluation framework}. \textit{BMC Geriatrics}. DOI: \doi{10.1186/s12877-025-06772-1}. \textit{WoS SCIE, Q1; first author.}

  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2025). \textbf{A community public health emergency resilience assessment framework based on contrastive learning and hyperbolic embedding}. \textit{Frontiers in Public Health}. DOI: \doi{10.3389/fpubh.2025.1651331}. \textit{WoS SSCI, Q1; first author.} Publisher PDF is bundled in \nolinkurl{representative-publications/}.

  \item Yanli Han; Quan Wen (2026). \textbf{Emotion Recognition in Literary Texts via an Attention-Guided Dual-Stream Gated Fusion Network}. \textit{IEEE Access}, 14, 67856--67869. DOI: \doi{10.1109/ACCESS.2026.3686065}. \textit{WoS SCIE; second author; corresponding author.}
\end{enumerate}

\section*{Attachment Note}
The repository includes a publisher PDF for the Frontiers in Public Health article. For the other selected works, the DOI links above should be used to access the official publisher pages and download the latest publisher PDFs when a university application system requires article uploads.

\end{document}
