\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.35cm]{geometry}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

\setmainfont{Times New Roman}
\definecolor{heading}{HTML}{003366}
\definecolor{subtle}{HTML}{555555}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\sloppy
\setlist[itemize]{leftmargin=1.15em, topsep=1pt, itemsep=0pt, parsep=0pt}
\setlist[enumerate]{leftmargin=1.35em, topsep=1pt, itemsep=0pt, parsep=0pt}

\titleformat{\section}{\normalsize\bfseries\color{heading}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{2pt}

\newcommand{\doi}[1]{\href{https://doi.org/#1}{\nolinkurl{#1}}}

\begin{document}

{\Large \textbf{Wen Quan}}\\[-1pt]
\textcolor{subtle}{Short CV for Lecturer Positions in Malaysia}\\[-1pt]
\href{mailto:wenquan@hngm.edu.cn}{wenquan@hngm.edu.cn} \,|\, 
\href{mailto:wenquan@student.usm.my}{wenquan@student.usm.my} \,|\, 
+86 156-4900-6328 \,|\, +60 12-938-6817\\
Zhengzhou, China \,|\, ORCID: \href{https://orcid.org/0009-0005-3975-8104}{0009-0005-3975-8104} \,|\,
\href{https://wenquan0816.github.io/schoolar-site/}{\nolinkurl{wenquan0816.github.io/schoolar-site}}

\section*{Profile}
Current Ph.D. student in Interior Design at Universiti Sains Malaysia with university teaching experience in interior design, decorative materials, architectural design, CAD/BIM, design software, and built environment studies. Research focuses on AI-assisted age-friendly environment assessment, evidence-based design, public health resilience, and design optimization. Record: 14 published journal articles, including 6 WoS SCIE/SSCI, 3 WoS ESCI, and 5 Scopus-indexed articles; 7 first-author articles; 5 PI-led research projects.

\section*{Education}
\begin{itemize}
  \item \textbf{Ph.D. in Interior Design}, School of Housing, Building and Planning, Universiti Sains Malaysia, 2021--Present.
  \item \textbf{M.Eng. in Architecture}, Henan University of Technology, 2014--2017. Specialization: Architectural Design and Theory.
  \item \textbf{B.Eng. in Architecture}, Anyang Normal University, 2009--2014. Dual Degree Program: Bachelor of Education.
\end{itemize}

\section*{Academic and Teaching Appointments}
\begin{itemize}
  \item \textbf{Current Ph.D. Student}, School of Housing, Building and Planning, Universiti Sains Malaysia, 2021--Present.
  \item \textbf{Secretary}, HBP Postgraduate Student Association, Universiti Sains Malaysia, 2025--Present.
  \item \textbf{Lecturer}, Henan Industry and Trade Vocational College, 2021--2023.
  \item \textbf{Part-time Lecturer}, Henan University of Animal Husbandry and Economy, 2019--2021.
  \item \textbf{Lecturer}, Easton International Art College, Zhengzhou University of Light Industry, 2017--2021.
\end{itemize}

\section*{Teaching Areas}
\begin{tabularx}{\textwidth}{>{\bfseries}p{0.22\textwidth}X}
Core studio/design & Interior Design; Architectural Design; Existing Building Renovation Design; Architectural Space Design \\
Technology/software & Decorative Materials; CAD; BIM Software Introduction; Photoshop; Illustrator; Software Rendering Design \\
Built environment & Building Structures; Architectural Surveying; Engineering Drawing; Architectural Investigation; History of Chinese and Foreign Architecture \\
Teaching context & Undergraduate courses; typical class size approximately 40 students \\
\end{tabularx}

\section*{Research Grants and Projects}
\begin{itemize}
  \item \textbf{Principal Investigator}, Comprehensive Aging-in-Place Renovation Framework for Legacy Residential Communities in Henan Province, Henan Provincial Social Science Research Fund, SKL-2022-608, 2022.
  \item \textbf{Principal Investigator}, Adaptive Renovation Strategies for Existing Long-term Care Facilities under COVID-19 Safety Protocols, Henan Provincial Department of Education, 2021-ZDJH-433, 2021.
  \item \textbf{Principal Investigator}, Interior Environment Design Strategies for Hospital Outpatient Departments in the Era of Telemedicine, Henan Provincial Social Science Research Fund, SKL-2020-1566, 2020.
  \item \textbf{Principal Investigator}, Integrated Healthcare-Housing Model for Community-Based Senior Living Facilities in Zhengzhou, Zhengzhou Federation of Social Sciences, JX20190146, 2018.
  \item \textbf{Principal Investigator}, Innovative Universal Design Strategies for New Community Development in Henan Province, Henan Provincial Social Science Research Fund, SKL-2018-490, First Prize, 2018.
\end{itemize}

\section*{Selected Publications}
\begin{enumerate}
  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2026). A LSTM-based model predictive control method for unlocking the potential of building energy flexibility in Malaysian commercial buildings. \textit{Scientific Reports}. DOI: \doi{10.1038/s41598-026-53501-8}. WoS SCIE, Q1; first author.
  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir; Yanting Wu; Chaojiang Hu (2026). AFLE-HIV: developing an age-friendly living environment assessment framework for elderly HIV-infected individuals in China. \textit{BMC Public Health}. DOI: \doi{10.1186/s12889-026-27748-9}. WoS SCIE, Q1; first author.
  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2026). Transforming vacant rural school buildings into age-friendly facilities under China's aging and low-fertility context: A natural language processing-based evaluation framework. \textit{BMC Geriatrics}. DOI: \doi{10.1186/s12877-025-06772-1}. WoS SCIE, Q1; first author.
  \item Quan Wen; Mazran Ismail; Muhammad Hafeez Abdul Nasir (2025). A community public health emergency resilience assessment framework based on contrastive learning and hyperbolic embedding. \textit{Frontiers in Public Health}. DOI: \doi{10.3389/fpubh.2025.1651331}. WoS SSCI, Q1; first author.
  \item Yanli Han; Quan Wen (2026). Emotion Recognition in Literary Texts via an Attention-Guided Dual-Stream Gated Fusion Network. \textit{IEEE Access}, 14, 67856--67869. DOI: \doi{10.1109/ACCESS.2026.3686065}. WoS SCIE; second author; corresponding author.
\end{enumerate}

\section*{Service, Certifications, and Referee}
\begin{itemize}
  \item Journal Reviewer, \textit{SAGE Open}; Academic Committee Member and Senior Project Review Expert, Zhongren Art Museum.
  \item Higher Education Teaching Qualification Certificate; Lecturer Certificate; National Computer Proficiency Examination Certification; Network Engineering Professional Certification.
  \item \textbf{Academic Referee:} Dr. Mazran bin Ismail, Senior Lecturer, Architecture, School of Housing, Building and Planning, Universiti Sains Malaysia. Email: \href{mailto:mazran@usm.my}{mazran@usm.my}. Relationship: Ph.D. supervisor.
\end{itemize}

\section*{Languages}
Chinese Mandarin: Native. English: Advanced academic and professional proficiency; TOEFL 86/120. Malay: Conversational proficiency.

\end{document}
